Understanding the impact of electronically-delivered parenting advice

### 2019-01-24 paper/cogsci2019/cogsci2019.Rmd
rewriting intro

- children learn through play -- physics, object features
Children want and need to play a lot: 
by interacting with other people or physcial objects, they explore, experiment and build up their understandings of how the world functions. 
Researches have suggested that play is important to learning,
"allowing children to imitate adult behaviors, practice motor skills, process emotional events, and learn much about their world."(Hirsh,2008)
## Guided Play Scaffolds Learning
- guided play activities can scaffold children's language and reasoning
What we cannot ignore, however,
is that children's efforts to explore the world are often "assisted and fostered by others who are more skillful than they are"(Kaye, 1970). 
With the help of an adult or "expert", children are able to engage with more advanced play and explore the functions of objects more.
These tutorial interactions have been shown to be a "a crucial feature of infancy and childhood"(Wood, 1970).
Thus, with the knowledge of both play and tutorial interactions, guided play, "where children actively engage in pleasurable and seemingly spontaneous activities under the direction of adults"(Hirsh,2008), 
have drawn researchers' interest. 
Weisberg showed that, with preschoolders, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes (Weisberg,Hirsh&Golinkoff, 2013).
Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills (Massey, 2013).

>>>>

Children spend a large portion of their waking time at play in their environment.
Playing with objects may allow them to discover hidden features, as well as to build a causal understanding of how the objects interact. 
Beyond learning object features, the laws of physics, and causal relationships (CITE), during play children practice motor skills that help them effectively navigate their world (Hirsh, 2008).
Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events (Hirsh, 2008).

## Guided Play Scaffolds Learning
Children's early play behaviors are often assisted by more skilled and knowledgeable play partners such as their caregivers and older siblings (Kaye, 1970). 
Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided (Vygotsky, 197X).
These tutorial interactions have been shown to be a "a crucial feature of infancy and childhood" (Wood, 1970).
Thus, with the knowledge of both play and tutorial interactions, guided play, "where children actively engage in pleasurable and seemingly spontaneous activities under the direction of adults" (Hirsh, 2008), 
have drawn researchers' interest. 
Weisberg showed that, with preschoolers, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes (Weisberg, Hirsh and Golinkoff, 2013).
Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills (Massey, 2013).
